The \emph{FThresholds} package for \emph{Macaulay2}

### 2019-06-04 Fsing/FThresholdsPaper/FThresholds.tex
Manually wrapped lines in verbose in the fpt section of the paper

i14 : fpt( f, Attempts => 1, DepthOfSearch => 3 ) -- the right-hand endpoint (nu+1)/p^e is the fpt

@@

i17 : fpt( f, Attempts => 2, DepthOfSearch => 3 ) -- the left-hand endpoint nu/(p^e-1) is the fpt

@@

i20 : fpt( f, DepthOfSearch => 3, Attempts => 3 ) -- an additional check sharpens the estimate

@@

i21 : fpt( f, DepthOfSearch => 3, Attempts => 4 ) -- and one more finds the exact answer

@@

i29 : fpt( f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true ) -- using FSignatures the answer improves a bit

@@

i30 : fpt( f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true, FRegularityCheck => true ) -- FRegularityCheck finds the answer

@@

i32 : timing numeric fpt( f, DepthOfSearch => 3, UseFSignature => true, FRegularityCheck => true )

@@

i33 : timing numeric fpt( f, Attempts => 5, DepthOfSearch => 3 ) -- a better answer in less time

@@

fpt failed to find the exact answer; try increasing the value of DepthOfSearch or Attempts.

>>>>

i14 : fpt( f, Attempts => 1, DepthOfSearch => 3 ) -- the right-hand

      endpoint (nu+1)/p^e is the F-pure threshold

@@

i17 : fpt( f, Attempts => 2, DepthOfSearch => 3 ) -- the left-hand endpoint

      nu/(p^e-1) is the F-pure threshold

@@

i20 : fpt( f, DepthOfSearch => 3, Attempts => 3 ) -- an additional check

      sharpens the estimate

@@

i21 : fpt( f, DepthOfSearch => 3, Attempts => 4 ) -- and one more finds

      the answer

@@

i29 : fpt( f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true ) --

      UseFSignature improves the answer a bit

@@

i30 : fpt( f, Attempts => 2, DepthOfSearch => 3, UseFSignature => true,

      FRegularityCheck => true ) -- FRegularityCheck finds the answer

@@

i32 : timing numeric fpt( f, DepthOfSearch => 3, UseFSignature => true,

      FRegularityCheck => true )

@@

i33 : timing numeric fpt( f, Attempts => 5, DepthOfSearch => 3 ) -- a better

      answer in less time

@@

fpt failed to find the exact answer; try increasing the value of

DepthOfSearch or Attempts.
